The imprint of global magma oceans on exoplanet demographics

### 2022-11-23 src/tex/ms.tex
add a paragraph on PLATO

\subsection{Signature and testability of the magma ocean hypothesis with the PLATO transit survey}

>>>>

\subsection{Signature and testability of the magma ocean hypothesis with the PLATO transit survey}
PLATO (PLAnetary Transits and Oscillation of stars) is an ESA mission designed to characterize terrestrial planets in the habitable zones of Sun-like stars, a goal to be achieved via long-term high-precision photometric monitoring of a sample of bright stars~\citep{Rauer2016}.
The PLATO team has released an estimate on the number of exoplanets that will be characterized in the course of the main survey mission (Matuszewski, priv. comm.).
In the FGK sample of the mission, a minimum of 500 Earth-sized (\SIrange{0.8}{1.25}{\rEarth}) planets are expected to be detected.
We base our assessment of PLATO's diagnostic power to test the magma ocean hypothesis on these estimates.
